%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{amssymb}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{makecell}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\courseworkSubheading}[2]{
	\vspace{-1pt}\item
	\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
	\end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{}{\Large Yiran Su}} & 
  {6805 Wood Hollow Dr,}\\
  {\href{mailto:yiransucdr@gmail.com}{$\lozenge$ yiransucdr@gmail.com}
  \href{https://www.linkedin.com/in/su-yiran-a2a146129/}{$\lozenge$ LinkedIn account} $\lozenge$ (512)-999-5939} & {Austin, TX} 
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
		{University of Texas at Austin}{Austin, TX, USA}
		{\makecell[tl]{\textbf{M.S.} in Engineering, \textbf{Software Engineering and System} track, ECE Dept. }}
		{Aug. 2019 - May. 2021 (expected)}
	\resumeSubheading
      {Sun Yat-sen University, School of Data and Computer Science}{Guangzhou, China}
      {\makecell[tl]{\textbf{B.E.} in Network Engineering~~~ 
      \textbf{Overall GPA}: 3.85/5.00, \textbf{Junior GPA}: 4.25/5.00\\
  	  \textbf{Course Highlights}: C++ programming, Data Structure and Algorithms, \\
  	  Operating System, Computer Network, Web Programming, Mobile Internet Programming Project}}
      {Aug. 2015 - Jun. 2019}
  \resumeSubHeadingListEnd

%-----------SKILLS-----------------
\section{SKILLS}
\textbf{Programming Language~}{C++, Python, Java, HTML5, CSS, JavaScript, Kotlin, Shell, SQL}\\
\textbf{Framework and Tools~}{React Native, Flask, PyTorch, Bootstrap, Git, MongoDB, Google Cloud Platform}


%-----------AWARDS AND HONORS-----------------
%\section{Awards And Honors}
%\resumeSubHeadingListStart
%\resumeSubItem{Innovative Design Award in the 2018 International Aerial Robotics Competition (2018 IARC)}{}
%\resumeSubItem{Honorable Award in the 2018 Mathematical Contest in Modeling (2018 MCM)}{}
%\resumeSubItem{The First Prize Scholarship of Sun Yat-sen University(Top 5\%)}{}
%\resumeSubHeadingListEnd

%-----------WORK EXPERIENCE-----------------
\section{Intern Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Tencent Inc.}{Shenzhen, China}
      {Perceptual Intelligence Group}{Sept. 2018 - Mar. 2019}
      \resumeItemListStart
      	\resumeItem
      	  {Developed a \textbf{pattern-based natural language parsing framework} in \textbf{Python} for a task-oriented Arena of Valor \textbf{chatbot} "Lu Bu (Lv, Bu)", while \textbf{reduced} the average latency by \textbf{27\%} to \textbf{less than 90 ms}.}
      	\resumeItem
          {Deployed the above framework on a \textbf{Tornado} Server, which handled more than \textbf{100k related requests} per day. }
        \resumeItem
          {Designed an \textbf{automatic} user log analyzer (\textbf{Python}) for the chatbot which is able to evaluate high frequency request, customer stickiness and new feature performance.}
      \resumeItemListEnd
          \resumeSubheading
      {Graduate Teaching Assistant}{Austin, TX}
      {EE 422C Software Design and Implementation (\textbf{Java}) II }{Jan. 2020 - May. 2020 (expected)}
      %\resumeItemListStart
      %\resumeItem
      %{Designed and graded assignments for more than 140 students. Held recitations for more than 40 students.}
      
      %\resumeItemListEnd
      \resumeSubHeadingListEnd
      
%-----------PROJECT EXPERIENCE-----------------
\section{Project Experience}
	\resumeSubHeadingListStart
	\resumeSubheading
	{Share Your Review}{Austin, TX}
	{Course project for EE 382V: Advanced Programming Tools at University of Texas at Austin}{Sept 2019 - Dec 2019}
	\resumeItemListStart
	\resumeItem
	{Participated this \textbf{full stack} project which allows users to post their book reviews and share to other apps. Users can create their own account, post book reviews, read reviews from others, subscribe certain categories and get corresponding update notifications. }
	\resumeItem
	{Designed a \textbf{MongoDB} database with \textbf{PyMongo} as our project database. Carried out \textbf{unit testing} for all APIs.
	}
	\resumeItem
	{Developed an \textbf{MVC} backend with \textbf{Flask} \& \textbf{Flask-RESTful}. Used \textbf{Firebase Storage} to store uploaded photos. }
	\resumeItem
	{Accomplished \textbf{web} frontend with \textbf{HTML/CSS/Bootstrap} and embedded it into our Flask-RESTful backend.}
	\resumeItem
	{Applied \textbf{Kotlin} in our \textbf{Android} frontend. Designed a \textbf{reusable cardview template} as a public method for other team members. Utilized \textbf{Camera API} and \textbf{Location API} to provide our users with diverse uploading choices. Used \textbf{Volley} to handle review creation request.  }
	\resumeItem
	{Implemented the \textbf{React Native} frontend with \textbf{Expo}. Beside of the points mentioned in the Android part, we enabled \textbf{notification} and \textbf{sharing} based on Expo components. }
	\resumeItemListEnd
	
	\resumeSubheading
	{Consistency Regularization (CR) in Natural Language Processing}{Austin, TX}
	{Research project for LIN 393: Computational Linguistic at University of Texas at Austin}{Sept 2019 - Dec 2019}
	\resumeItemListStart
	\resumeItem
	{Embeded the semi-supervised learning concept \textbf{consistency regularization} into supervised learning NLP tasks, in order to make the supervised model \textbf{more robust to it's predictions}. }
	%\resumeItem
	%{Proposed \textbf{random delete} (fast perturbation solution) and \textbf{paraphrase substitution} (semantical perturbation solution)to  perturb input data. }
	\resumeItem
	{Implemented the new \textbf{TextCNN-CR} model with \textbf{PyTorch}. Scored \textbf{77.06\%} in accuracy on MR (Movie Review Data) binary classification dataset, compared with the  75.33\% accuracy of original TextCNN model.}
	\resumeItemListEnd

\resumeSubheading
{International Aerial Robotics Competition}{Guangzhou \& Beijing, China}
{ \textbf{Innovative Design Award}, Computer Vision Group member}{Sept. 2017 - Aug. 2018}
\resumeItemListStart

\resumeItem
{Designed an object \textbf{detection} and \textbf{location} system for an aerial robot.}
\resumeItem
{Constructed an \textbf{SVM} ground robot detector in \textbf{C++} for our system by writing a \textbf{self-implemented} Histogram of Oriented Gradient descriptor (\textbf{HOG descriptor}) and applying \textbf{OpenCV}’s related packages.}

\resumeItemListEnd	  
  \resumeSubHeadingListEnd
  
  

%
%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
